---
title: "Individual Analysis for Messier, Reif, and Marvel 2024"
output:
  html_document:
    df_print: paged
---

# About 
# TODO Specify any pre-amble information


# Setup

```{r}
library(targets)
tar_destroy() # Start fresh.
```

# Functions

For the GeoTox pipeline analysis of individual level data, the functions are in `./my_target_funs.R`. T


# _targets.R file for pipeline
To formalize our three targets, we express the computation in a special configuration file called `_targets.R` at the project's root directory. The role of `_targets.R` is to

1. Load any functions and global objects that the targets depend on.
2. Set any options, including packages that the targets depend on.
3. Declare a list of targets using `tar_target()`. The `_targets.R` script must always end with a list of target objects.


```{r}
library(targets)
tar_edit()
```

Functions `tar_make()`, `tar_validate()`, `tar_manifest()`, `tar_glimpse()`, and `tar_visnetwork()` all need `_targets.R`. `_targets.R` lets these functions invoke the pipeline from a new external R process in order to ensure reproducibility.

```{r}
tar_validate() # Looks for errors.
```

```{r}
tar_manifest(fields = "command") # Data frame of target info.
```

```{r}
tar_glimpse() # Interactive dependency graph.
```

# Dependency relationships


That means the order you write your targets does not matter. Even if you rearrange the calls to `tar_target()` inside the list, you will still get the same workflow.

`tar_visnetwork()` also includes functions in the dependency graph, as well as color-coded status information.

```{r}
tar_visnetwork()
```

# Run the pipeline.

Everything we did so far was just setup. To actually run the pipeline, use the `tar_make()` function. `tar_make()` creates a fresh new reproducible R process that runs `_targets.R` and executes the correct targets in the correct order (from the dependency graph, not the order in the target list).

```{r}
tar_make()
```
# View the plot

```{r}
tar_load(plot_mixture)
tar_read(plot_mixture)
```

# Inspect the results

Targets `churn_data` and `churn_recipe` now live in a special `_targets/` data store.

```{r}
list.files("_targets/objects")
```

